iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-28 manuscript/main.tex
R code. Layout web link to allen app

\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{f1000_styles}
\usepackage{url}

@@

\subsection*{Single-cell plate-based RNA-seq}
% TODO: better title, or do we drop this allen section altogether?
We demonstrate the application of iSEE to examine a subset of 379 cells from of mouse visual cortex \citep{tasic2016allen}.
This example can be reproduced also by calling

library(iSEE)
example(iSEE, ask = F)

% TODO: embed the allen demo data set
\url{http://shiny.imbei.uni-mainz.de:3838/iSEE/}

>>>>

\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{f1000_styles}
\usepackage{url}
\usepackage{listings}

@@

\subsection*{Single-cell plate-based RNA-seq}
% TODO: better title, or do we drop this allen section altogether?
We demonstrate the application of iSEE to examine a subset of 379 cells from of mouse visual cortex \citep{tasic2016allen}.

Link: \url{http://shiny.imbei.uni-mainz.de:3838/iSEE/}

This particular example can be reproduced locally after installation of the iSEE package with the following code:

\begin{lstlisting}[language=R]
library(iSEE)
example(iSEE, ask = F)
\end{lstlisting}
